\documentclass{article}
\usepackage{enumitem}

% Don't indent paragraphs
\setlength\parindent{0pt}

% meta data
\newcommand{\chapter}{1.3}
\newcommand{\authorname}{Amo DelBello}
\newcommand{\classdescription}{MATH 1350-D2}
\newcommand{\classname}{Introduction to Statistics, Fall 2022}
\newcommand{\assignment}{\chapter\ Book Assignment}

% headers
\newcommand{\problem}[1]{\vspace{5ex}\section*{\chapter-#1}}
\newcommand{\solution}{\subsection*{Solution}}

\title{\classdescription\ \\ \classname\ \\ $\ $ \\ \assignment}
\author{\authorname}
\date{\today}

\begin{document}
\maketitle


\problem{3}
Replication was used effectively because the experiment was applied to large enough groups to yield satisfactory results.


\problem{6}
The study is an observational study because the data come from a survey not from the observed effects of an applied treatment.


\problem{9}
Systematic sampling is used because sample data is collected at regular intervals


\problem{12}
Stratified sampling is used because the population is first subdivided into male and female groups and then random samples are taken from those strata.


\problem{15}
Stratified sampling is used because books are randomly selected from specific subdivisions.


\problem{18}
Cluster sampling is used because all voters were surveyed from specific, randomly chosen polling places.


\problem{21}
The study is an observational study. A major problem is that the sample has a high probability of bias because it came from volunteer responses of internet users. Thus, the results probably do not reflect the population as a whole.


\problem{24}
The study is an observational study. A major problem is that the sample size is very small.


\problem{27}
The study is an observational study. A major problem is the respondents may feel embarrassed or uncomfortable giving honest responses due to the sensitive nature of the questions.


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
